When are Fuzzy Extractors Possible?

### 2014-09-16 trunk/info-bounds/FuzzyExtPossibility.tex
writing down distribution aware impossibility
editing intro

\begin{theorem}
Let $n$ be a security parameter.  There exists a family of distributions $\mathcal{V}$ such that for each element $W\in \mathcal{V}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{V}, \tilde{m}, t)$-secure sketch with error $\delta < 1/4$ for $\tilde{m} =\omega(1)$ for $t\ge 4$.  \bnote{finish proof}
\end{theorem}

@@

Consider some $p\in A_{ss}$.  We now show that $H_0(V | p) \le n-\log |B_t|$.  Note for the true value $w$ sketched $\{w' | \dis(w, w') \le t \wedge \rec(w', p) \neq w] \le 2\delta$.  Thus for every value in $V|p$ this is also true.  This makes the support of $V|p$ a $(t, 2\delta)$-Shannon code~(see \defref{def:shannon-code}).  In particular, this implies that for all $w_1, w_2 \in V|p$, $\dis(w_1, w_2)\ge t$~(since $2\delta< 1/2$).  That is $V|p$ is a set with minimum distance at least $t$.  By the Singleton bound, this implies that $H_0(V | p) \le (\ell -t )|\mathbb{F}|$.  Averaging over $p$ one has that $\tilde{H}_0(V|P) \le (\ell -t +1) \log|\mathbb{F}| +1$.
%By the Markov inequality, 
%\[
%\forall w, w^*, \Pr_{p \leftarrow \sketch(w)} [ \Pr[\rec(w^*, p) = w] \le 1-2\delta ] < \delta /2.
%\]
%That is, for most $p$, $\Pr[\rec(w^*, p) = w] > 1-2\delta>1/2$.
%
%Outline of what I want to say.
%\begin{itemize}
%\item Suppose we are at some good sketch value, that is, the sketch decodes well for $w^*$ close to the true value $w$.
%\item Then for the true value that was sketched, for most neighbors $w^*$ of $w$, $\Pr[\rec(w^*, p) =w] >1/2$.  
%\item For a value $w'$ to be in the support of $W | P=p$, it must be for all neighbors of $\Pr[\rec( w', p) =w ]>1/2$.
%\item This implies that if $w_1, w_2 \in W|P = p$, then $\dis (w_1, w_2)\ge t$.
%\item Conditioned on $P=p$, $W| P=p$ is a good code for random errors.
%Consider some subset $G\subseteq supp(W| P=p)$ with $\Pr (W| P=p \in G)\ge 1/2$.  Then for all $w\in G$ the probability they recover correctly is at least $1-4\delta$~(by another application of Markov).  
%\item This, means that the size of $|G|$ is at most $n -\log |B_t|$.
%\end{itemize}
\end{proof}
We showed that for most values of $\sketch$ many values of $V$ are removed from the support.  We now show that the information contained in $Z$ is enough to nearly determine the actual sketched value.

@@

This means that the $\sketch$ algorithm include points for possible $Z$ values~(other than $v$) and these values are disjoint.  The optimum strategy is to include these values uniformly from different $Z$ values.\bnote{prove this}  This means that
\begin{align*}
\Hav(V | \sketch(V), Z) &\le \tilde{H}_0(V | \sketch(V) )- \log H_0(Z | V)\\
&\le (\ell-t+1)\log |\mathbb{F}|+1 - \log (|\mathbb{F}|-1)^{\ell-1}/|\mathbb{F}|\\
&\le (\ell-t+2)\log |\mathbb{F}| - (\ell-1) \log (|\mathbb{F}|-1)+1\\
&\le (\ell-t+2)\log |\mathbb{F}| - (\ell-2) \log |\mathbb{F}|+1\\
&\le \Theta(1)
\end{align*}
 Where the last line follows for $t\ge 4$.  The fourth line follows from the third as long as $|\mathbb{F}|????$\bnote{fix this}
 \end{proof}
%\begin{lemma}
%$\Hav(V| P , Z) = \Theta(1)$
%\end{lemma}
%\begin{proof}
%Consider some fixed $p$.
%If $Z$ is universal then $\forall w_1, w_2 \in V|P=p, w_1\neq w_2$\bnote{why should $Z$ be universal for the entire range, I get for each coordinate.}
%\[
%\Pr[Z(w_1) = Z(w_2)] = \frac{1}{|Z|}.
%\]
%Then by the union bound, 
%\[
%\Pr[\exists w_1\neq w_2 \wedge Z(w_1) = Z(w_2)]\le \frac{ 2^{H_0(V|P=p)}}{|Z|}.
%\]
%\bnote{need to average across $P$}
%\bnote{I'm confused about what we mean by $Z$ being universal here.}
%\bnote{working here!}
%\end{proof}
%
%\bnote{stopped here}
\end{proof}

@@

Canetti et al.~\cite[XXXX]{canetti2014key} construct computational fuzzy extractors for this family of distributions~(as long $\mathbb{F}$ is large enough).\bnote{fill in right theorem number}  This result presents a contrast between what is possible for sketches and fuzzy extraction.

>>>>

\begin{theorem}
\label{thm:imposs sketch}
Let $n$ be a security parameter.  There exists a family of distributions $\mathcal{V}$ such that for each element $W\in \mathcal{V}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{V}, \tilde{m}, t)$-secure sketch with error $\delta < 1/4$ for $\tilde{m} =\omega(1)$ for $t\ge 4$.  \bnote{finish proof}
\end{theorem}

@@

Consider some $p\in A_{ss}$.  We now show that $H_0(V | p) \le n-\log |B_t|$.  Note for the true value $w$ sketched $\{w' | \dis(w, w') \le t \wedge \rec(w', p) \neq w] \le 2\delta$.  Thus for every value in $V|p$ this is also true.  This makes the support of $V|p$ a $(t, 2\delta)$-Shannon code~(see \defref{def:shannon-code}).  In particular, this implies that for all $w_1, w_2 \in V|p$, $\dis(w_1, w_2)\ge t$~(since $2\delta< 1/2$).  That is $V|p$ is a set with minimum distance at least $t$.  By the Singleton bound, this implies that $H_0(V | p) \le (\ell -t+1 )|\mathbb{F}|$.  Averaging over $p$ one has that $\tilde{H}_0(V|P) \le (\ell -t +1) \log|\mathbb{F}| +1$.
%By the Markov inequality, 
%\[
%\forall w, w^*, \Pr_{p \leftarrow \sketch(w)} [ \Pr[\rec(w^*, p) = w] \le 1-2\delta ] < \delta /2.
%\]
%That is, for most $p$, $\Pr[\rec(w^*, p) = w] > 1-2\delta>1/2$.
%
%Outline of what I want to say.
%\begin{itemize}
%\item Suppose we are at some good sketch value, that is, the sketch decodes well for $w^*$ close to the true value $w$.
%\item Then for the true value that was sketched, for most neighbors $w^*$ of $w$, $\Pr[\rec(w^*, p) =w] >1/2$.  
%\item For a value $w'$ to be in the support of $W | P=p$, it must be for all neighbors of $\Pr[\rec( w', p) =w ]>1/2$.
%\item This implies that if $w_1, w_2 \in W|P = p$, then $\dis (w_1, w_2)\ge t$.
%\item Conditioned on $P=p$, $W| P=p$ is a good code for random errors.
%Consider some subset $G\subseteq supp(W| P=p)$ with $\Pr (W| P=p \in G)\ge 1/2$.  Then for all $w\in G$ the probability they recover correctly is at least $1-4\delta$~(by another application of Markov).  
%\item This, means that the size of $|G|$ is at most $n -\log |B_t|$.
%\end{itemize}
\end{proof}
We showed that for most values of $\sketch$ many values of $V$ are removed from the support.  We now show that the information contained in $Z$ is enough to nearly determine the actual sketched value.

@@

This means that the $\sketch$ algorithm include points for possible $Z$ values~(other than $v$) and these values are disjoint.  The optimum strategy is to include these values uniformly from different $Z$ values.\bnote{prove this}  This means that
\begin{align*}
\tilde{H}_0(V | \sketch(V), Z) &\le \tilde{H}_0(V | \sketch(V) )- \log H_0(Z | V)\\
&\le (\ell-t+1)\log |\mathbb{F}|+1 - \log (|\mathbb{F}|-1)^{\ell-1}/|\mathbb{F}|\\
&\le (\ell-t+2)\log |\mathbb{F}| - (\ell-1) \log (|\mathbb{F}|-1)+1\\
&\le (\ell-t+2)\log |\mathbb{F}| - (\ell-2) \log |\mathbb{F}|+1\\
&\le \Theta(1)
\end{align*}
 Where the last line follows for $t\ge 4$.  The fourth line follows from the third as long as $|\mathbb{F}|????$\bnote{fix this}\bnote{add more to this}
 \end{proof}

 \thref{thm:imposs sketch} follows using the change of quantifiers in \corref{cor:no fuzz for dist}.
%\begin{lemma}
%$\Hav(V| P , Z) = \Theta(1)$
%\end{lemma}
%\begin{proof}
%Consider some fixed $p$.
%If $Z$ is universal then $\forall w_1, w_2 \in V|P=p, w_1\neq w_2$\bnote{why should $Z$ be universal for the entire range, I get for each coordinate.}
%\[
%\Pr[Z(w_1) = Z(w_2)] = \frac{1}{|Z|}.
%\]
%Then by the union bound, 
%\[
%\Pr[\exists w_1\neq w_2 \wedge Z(w_1) = Z(w_2)]\le \frac{ 2^{H_0(V|P=p)}}{|Z|}.
%\]
%\bnote{need to average across $P$}
%\bnote{I'm confused about what we mean by $Z$ being universal here.}
%\bnote{working here!}
%\end{proof}
%
%\bnote{stopped here}
\end{proof}

@@

Canetti et al.~\cite{canetti2014key} construct computational fuzzy extractors for this family of distributions when $\mathbb{F}$ is large enough.\bnote{fill in right theorem number}  This result presents a contrast between what is possible for sketches and fuzzy extraction.
